---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# Automated Retrieval of Disaster Event Data

<!-- badges: start -->
```{r, include = FALSE}
usethis::use_cran_badge()
usethis::use_lifecycle_badge("maturing")
```
[![CRAN status](https://www.r-pkg.org/badges/version/disastr.api)](https://CRAN.R-project.org/package=disastr.api)
[![Travis build status](https://travis-ci.com/chris-dworschak/disastr.api.svg?branch=master)](https://travis-ci.com/github/chris-dworschak/disastr.api)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

This small package provides functionality to access and manage the application programming interface (API) of the [United Nations Office for the Coordination of Humanitarian Affairs' (OCHA) ReliefWeb disaster events](https://reliefweb.int/disasters/). The function `disastr.api()` makes it easy to retrieve a user-defined sample (or all of the available data) from ReliefWeb, enabling a seamless integration of regular data updates into the research work flow.




## Installation

You can install the released version of disastr.api from [CRAN](https://CRAN.R-project.org) with: 

``` r
install.packages("disastr.api")
```

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chris-dworschak/disastr.api") # downloads and installs the package
```


## Example

Using `disastr.api` is straight forward. To download data on, for example, the last 30 disaster events, you can supply:


```{r example}
library(disastr.api) # loads the package

my.data.frame <- disastr.api( # stores retrieved disaster events in object my.data.frame
  limit = 30)

head(my.data.frame) # returns the first five observations of the ACLED sample
```
